%resume document class
\documentclass{res}

\usepackage{hyperref}  % for links to email and LinkedIn
\usepackage{helvetica} % using helvetica postscript font
%\usepackage{newcent}   % another postscript font option
\usepackage{geometry}

% can fiddle with page margins as stuff is added/deleted
%\setlength{\textheight}{9.7in}
%\addtolength{\topmargin}{-.7in}
\newgeometry{left=1.5cm,bottom=1cm,top=1.6cm}
%\newsectionwidth{20pt}
\hoffset=0.1in

\newcommand{\vb}{\; | \;}

\begin{document} 
\name{\LARGE MICHAEL S. SAUGSTAD}
                                  
\begin{resume}
\vspace{-5pt}
{\large % increasing font size of whole document
  % link to email, phone number, link to LinkedIn
  \begin{center}
    \href{mailto:saugstad@cs.umd.edu}{saugstad@cs.umd.edu} $\vb$
    (262) 751-5697 $\vb$
    \href{https://github.com/misaugstad}
         {github.com/misaugstad}
  \end{center}

  \vspace{-2pt}
  \section{\hspace{0.2in}EDUCATION}
    \vspace{3pt} % UMaryland PhD
    {\bf University of Maryland, College Park}, College Park, MD\\
    \begin{minipage}{5.6in}
      M.S. in Computer Science
    \end{minipage}
    \begin{minipage}{2in}
      May 2018
    \end{minipage}
    GPA: 4.0

    \vspace{-5pt} % Vassar College Undergrad
    {\bf Vassar College}, Poughkeepsie, NY\\
    \begin{minipage}{5.6in}
      B.A. in Mathematics and Statistics, Computer Science
    \end{minipage}
    \begin{minipage}{2in}
      May 2016
    \end{minipage}
    GPA Overall: 3.79  Majors: 3.86

  \vspace{-1pt}
  \section{\hspace{0.3in}RELEVANT EXPERIENCE}
    \vspace{-3pt}
    \begin{tabbing}
      \hspace{5.65in}\=  \kill % sets right column  location
      {\bf Research Assistant}
      \>June 2017 - Present\\
      University of Maryland Computer Science Department, College Park, MD\\     
    \end{tabbing}
    \vspace{-24pt}      % suppress blank line after tabbing
    \begin{list}{\bf{-}}{}
      \setlength{\itemsep}{-2pt}
      \item Leading software development on
            \href{http://sidewalk.umiacs.umd.edu/}{Project Sidewalk}, an online tool for large-\\
            scale virtual auditing of urban accessibility; working with
            \href{http://www.cs.umd.edu/~jonf/}{Prof Jon Froehlich}.
      \item Maintaining and updating the tool's Scala/Postgres back-end infrastructure.
      \item Leading data analysis for the project, using R and Javascript.
      \item Mentoring 3 undergraduate and highschool students on the team.
    \end{list}

    \vspace{-12pt}
    \begin{tabbing}
      \hspace{5.65in}\=  \kill % sets right column  location
      {\bf Teaching Assistant}
      \>Aug 2016 - May 2017\\
      University of Maryland Computer Science Department, College Park, MD\\     
    \end{tabbing}
    \vspace{-24pt}      % suppress blank line after tabbing
    \begin{list}{\bf{-}}{}
      \setlength{\itemsep}{-2pt}
      \item Mentored and assisted 75 students with Java and OOP concepts.
    \end{list}
    
    \vspace{-12pt}
    \begin{tabbing}
      \hspace{5.65in}\=  \kill % sets right column  location
      {\bf Research Assistant}
      \>Jan 2015 - May 2016\\
      Vassar College Computer Science Department, Poughkeepsie, NY\\     
    \end{tabbing}
    \vspace{-24pt}      % suppress blank line after tabbing
    \begin{list}{\bf{-}}{}
      \setlength{\itemsep}{-2pt}
      \item Implemented reactive indoor navigation using dynamical systems.
      \item Integrated existing Python code base into the ROS ecosystem.
      \item Redesigned robot's vision to utilize Kinect depth sensor.
    \end{list}

    \vspace{-12pt}
    \begin{tabbing}
      \hspace{5.65in}\=  \kill % sets right column  location
      {\bf Research Intern - Quality of Life Technology NSF REU}
      \>May 2015 - Aug 2015\\
      Carnegie Mellon University Robotics Institute, Pittsburgh, PA\\     
    \end{tabbing}
    \vspace{-24pt}      % suppress blank line after tabbing
    \begin{list}{\bf{-}}{}
      \setlength{\itemsep}{-2pt}
      \item Developed C++ software for socially acceptable autonomous robot navigation.
    \end{list}

    \vspace{-12pt}
    \begin{tabbing}
      \hspace{5.65in}\=  \kill % sets right column  location
      {\bf Programming Instructor}
      \>June 2014 - Aug 2014\\
      iD Tech Camps at MIT, Boston, MA\\     
    \end{tabbing}
    \vspace{-24pt}      % suppress blank line after tabbing
    \begin{list}{\bf{-}}{}
      \setlength{\itemsep}{-2pt}
      \item Taught courses in game design and Java to 6-13 year olds.
    \end{list}
  
  \vspace{-1pt}
  \section{\hspace{0.2in}COMPUTER SKILLS}
    \vspace{3pt}
      Proficient: R, Scala/Java, Python, Javascript, C++, Postgres, SQL, LaTeX, ROS, Linux\\
      Familiar: Haskell, OpenMP, MPI, Play, C/UPC, Scheme, Assembly, Occam-Pi, Prolog\\

  \vspace{-16pt}
  \section{\hspace{0.2in}AWARDS AND LEADERSHIP}
    \vspace{-3pt}
    \begin{tabbing}
      \hspace{5.65in}\=  \kill % sets right column  location
      {\bf Recipient}, Dean's Fellowship, Dept of Computer Science, UMD\>
          Aug 2016, 2017\\
      {\bf Recipient}, Janet Holdeen-Adams Prize, Dept of Computer Science, Vassar\>
          May 2016\\
      {\bf Co-chair}, Computer Science Majors Committee, Vassar\>
          Sept 2014 - May 2015\\
      {\bf Captain and Treasurer}, Quidditch Team, Vassar\>
          Sept 2013 - May 2014\\
      {\bf Co-founder}, Quidditch Program -- Parks \& Recreation Dept, Waukesha, WI\>
           June 2013 - Aug 2013\\
    \end{tabbing}
} % end large
\end{resume}
\end{document}